\begin{spacing}{1}
\linespread{1}



\newpage
\section*{Acknowledgments}
I want to thank Professor Dagan Karp at Harvey Mudd College, my undergraduate adviser, for being an amazing 
mentor and for providing me extremely helpful advice and support during my time at Harvey Mudd.
Professor Karp also supervised an independent study for which a large portion of this text originated from.

I also want to thank Professor Vin de Silva at Pomona College, my undergraduate thesis adviser.
Through Professor de Silva's humility and patience I learned a great deal of category theory and many tecniques
how to write mathematics clearly. I also would have never produced Section \ref{section:coherence_theorem}
or the chapter on Persistence Modules without his feedback.

I'd also like to thank Daniel Donnelley Jr for catching dozens of typos and 
statements that were plain wrong; errors that could only have been caught 
through a thorough reading. Donnelley also offered extremely helpful feedback, and
suggested many sentence revisions and section restructurings which were all 
in the best interest of increasing the readability of this text.  

\section*{About the Cover}
The cover of the text is a long exposure shot I took from a popular 
hiking trail on top of Mount Baldy in Claremont, CA. You can probably 
tell neither the camera nor the photographer were very good, and that there's a lot 
of light pollution in Southern California. 


\newpage
{\centering \huge\textbf{Warning!}}
\\
\\

This is a work in progress, and there are lots of typos. Some sections 
are being reorganized. I probably won't be ``finished'' for a long time.
\texttt{ltrujillo@hmc.edu} .


\end{spacing}
